%-----------EXPERIENCE-----------%
\section{\faIcon{briefcase} \textbf{ Experience}}
    \resumeSubHeadingListStart
    
        \resumeSubheading
        {Metro Analytics}{Atlanta, GA}
        {Transportation Planner/Analyst - Full Time}{Jun 2023 -- Present}
        \resumeItemListStart
            \resumeItem{Conducted research and analysis to advance transportation decision-making, including evaluating economic, social, safety, and equity impacts, developing best practices, and implementing innovative planning strategies.}
            \resumeItem{Utilized transportation performance metrics, safety data, economic statistics, modeling platforms, and GIS to analyze and visualize system performance and accessibility, while producing high-quality consulting deliverables such as reports and presentations.}
            \resumeItem{Collaborated with diverse stakeholders, mentored junior staff, and participated in business development activities to address complex policy, safety, and planning questions, and deliver innovative solutions.}
            \resumeItem{Projects:
                \begin{itemize}[label=-]
                    \item \textbf{Benefit-Cost Analysis:} \textit{Ohio DOT Cleveland CCG3A Intersection, Missouri DOT STIP 2024-2027 \& STIP 2025-2028}
                    \item \textbf{Economic Impact Analysis:} \textit{Utah’s Unified Plan 2023-2050, Utah Transit Authority 2023-2050}
                    \item \textbf{Metropolitan Transportation Plans (MTP):} \textit{Valdosta-Lowndes MPO 2050 MTP, DARTS 2050 MTP, Bowling Green-Warren County 2050 MTP, Greater Dalton 2050 MTP}
                    \item \textbf{Freight Plans:} \textit{Stonecrest Freight Cluster Plan, ARTS Regional Freight Plan, TMACOG Freight Profile}
                    \item \textbf{Resiliency Plans:} \textit{Albany-DARTS Resiliency Plan}
                    \item \textbf{National Research:} \textit{NCHRP 08-146: Integrating Resiliency into Transportation System Operations}
                \end{itemize}
            }
        \resumeItemListEnd
        
        \resumeSubheading
        {University of Utah}{Salt Lake City, UT}
        {Graduate Teaching Assistant - Department of City and Metropolitan Planning}{Aug 2021 -- May 2023}
        \resumeItemListStart
            \resumeItem{Assisted in teaching both undergraduate and graduate courses across five academic terms, supporting course content delivery, managing assignments, and enhancing student learning experiences through regular office hours and personalized guidance.}
            \resumeItem{Led classroom workshops for 48 graduate students on community and regional analysis, focusing on demographic and economic assessments, while utilizing advanced Excel techniques for data analysis and visualization.}
        \resumeItemListEnd

        \resumeSubheading
        {}{}
        {Graduate Research Assistant - Department of City and Metropolitan Planning}{May 2022 -- Aug 2022}
        \resumeItemListStart
            \resumeItem{Conducted comprehensive statistical and empirical analyses using R and SPSS to evaluate resident survey data for the "\href{https://thrivinginplaceslc.org/}{\textit{Thriving in Place}}" initiative, focusing on housing affordability trends in Salt Lake City to identify factors contributing to resident displacement.}
            \resumeItem{Developed policy recommendations based on research findings to preserve and increase housing availability, supporting anti-displacement strategies aimed at helping residents thrive amidst urban growth and gentrification, focusing on Wasatch Hollow and Liberty Wells neighborhoods.}
        \resumeItemListEnd
    
        \resumeSubheading
        {}{}
        {Student Researcher - Energy \& Geoscience Institute (EGI)}{June 2022 -- Aug 2022}
        \resumeItemListStart
            \resumeItem{Collaborated with geoscience researchers to provide geospatial analysis and visualizations for global and regional mining operations, supporting data-driven decision-making in resource exploration.}
            \resumeItem{Developed and processed comprehensive geospatial datasets, georeferenced historic mining maps, and integrated geological data for mining regions in Utah and Wyoming.}
        \resumeItemListEnd
    
        \resumeSubheading
        {Prabal Thapa Architects}{Kathmandu, Nepal}
        {Architecture Intern \& Associate Architect - Full Time}{Oct 2016 - Apr 2017, Jun 2020 - Jul 2021}
        \resumeItemListStart
            \resumeItem{Developed detailed conceptual design drawings for a variety of architectural projects, including hospitality developments in Ghandruk and Nagarkot, and residential and institutional projects in Surkhet, Chitwan, and Kathmandu.}
            \resumeItem{Led the development of architectural plans and graphical communications using 2D and 3D visualization, ensuring designs met client expectations and project objectives while fostering strong client relationships through effective communication and tailored solutions.}
            \resumeItem{Mentored and guided junior staff in advanced design techniques and software applications, enhancing their skills and contributing to overall project success.}
        \resumeItemListEnd
    
        \resumeSubheading
        {Institute of Engineering, Research Training and Consultancy Services Unit}{Lalitpur, Nepal}
        {Associate Architect - Freelance}{Sep 2020 -- Jun 2021}
        \resumeItemListStart
            \resumeItem{Led the design team in developing the Masterplan for Padma Kanya Multiple Campus, ensuring alignment with strategic goals and optimizing space utilization to support the institution's growth.}
            \resumeItem{Produced architectural drawings and digital models, provided planning-level cost estimates, and effectively communicated design concepts and progress to stakeholders, facilitating informed decision-making.}
        \resumeItemListEnd
    
        \resumeSubheading
        {Urban Park Pvt. Ltd.}{Lalitpur, Nepal}
        {Junior Architect - Full Time}{Jan 2019 -- Jun 2020}
        \resumeItemListStart
            \resumeItem{Contributed to architectural design and urban planning projects across residential, institutional, and hospitality sectors, including the Film City Masterplan in Dolakha and the ICT Center for Tulsipur’s Smart City initiative.}
            \resumeItem{Led the development of innovative masterplans, ensuring design solutions aligned with strategic objectives and enhancing project outcomes through creative and functional design.}
            \resumeItem{Developed comprehensive project reports for infrastructure initiatives across Terai and Mid Hill regions, supporting effective urban planning within Nepal's Integrated Urban Development Plan (IUDP) and promoting sustainable growth in newly established municipalities.}
        \resumeItemListEnd
    
        \resumeSubheading
        {Archetype Design Consult Pvt. Ltd.}{Kathmandu, Nepal}
        {Architect - Freelance}{Jun 2018 -- Jan 2020}
        \resumeItemListStart
            \resumeItem{Led the conceptualization and execution of major conservation projects, including the Conservation Masterplan for the Sindhuligadhi Area and the Pashupatinath Temple Complex, adhering to international heritage standards.}
            \resumeItem{Conducted in-depth research, developed detailed inventories of historical assets, and produced comprehensive project reports and digital models, effectively communicating conservation strategies and balancing preservation with sustainable development.}
        \resumeItemListEnd
    
    \resumeSubHeadingListEnd